The Eclipse Integrated Computational Environment

### 2017-05-23 src/content.tex
Touched up the conclusions to address some of Sam's suggestions. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

Workflows for computational scientists in modeling and simulation differ
greatly from experimentalists or those who primarily interact with
grid-based workflow management systems. This work presented the Eclipse
Integrated Computational Environment (ICE) and described how it has
been used to address interdisciplinary problems in modeling and
simulation for energy science. One interesting avenue for future
exploration is coupling or integrating ICE with other workflow tools
such as Aiida, Triquetrum, Kepler and Pegasus. It remains as abundantly
clear now as it was in Mandal's 2007 paper that the best of all workflow
management tools will be needed to address high-performance computing
problems at the exascale and beyond.

>>>>

Workflows for computational scientists in modeling and simulation differ
greatly from experimentalists or those who primarily interact with
grid-based workflow management systems, which has driven the creation of
additional workflow management systems to meet those needs. This work 
presented the Eclipse Integrated Computational Environment (ICE) and 
described how it has been used to address interdisciplinary problems in 
modeling and simulation for energy science. Of particular note is the
difference in architecture between a workflow management system focused
on modeling and simulation compared to those focused on grids. ICE's broad
applicability across a number of topics in energy science suggests that
there are opportunities for these systems in general. Finally, one 
interesting avenue for future exploration is coupling or integrating ICE 
with other workflow tools such as Aiida, Triquetrum, Kepler and Pegasus,
which would make it possible to combine the best of grid and modeling and
simulation workflows to address greater challenges.
